19th International Satisfiability Modulo Theories Competition (SMT-COMP 2024): Rules and Procedures

### 2024-05-09 rules/rules24.tex
Clarify persistent storage.

\header{Persistent State.}
%
Solvers may create and write to files and directories during the
course of an execution, but they must not read such files back during
later executions.  Each solver is executed with a temporary directory
as its current working directory.  Any generated files should be
produced there (and not, say, in the system's \texttt{/tmp}
directory).  The \executionservice sets a limit on the amount of disk
storage permitted---typically 20\,GB.  See the user guide for the
\executionservice for more information.  The temporary directory is
deleted after the job is complete.  Solvers must not attempt to
communicate with other machines, e.g., over the network.
\todo{What are the limits for BenchExec? Do we set limits ourselves?}

>>>>

\header{Persistent State.}
%
Solvers may create and write to files and directories during the
course of an execution, but they must not read such files back during
later executions. This is ensured by BenchExec by executing each solver
with the whole filesystem mounted as read-only with an overlay writeable
layer that is mounted as a RAM disk. Any generated files will be therefore
written to the RAM disk. The used storage is counted into the
memory limit. The temporary overlay layer is deleted after the job is complete.
Solvers must not attempt to communicate with other machines, e.g., over the network.
